Satisfiability Modulo Theories Competition (SMT-COMP) 2011: Rules and Procedures

### 2015-02-16 rules/rules11.tex
I believe this was the final (official) version of the 2011 rules.

\date{}

@@

@@

\header{Timeouts.}
A time limit is set for the whole execution of each application
benchmark (consisting of multiple queries).

@@

\begin{itemize}
\item QF\_UF: uninterpreted functions.
\item QF\_RDL: real difference logic.
\item QF\_IDL: integer difference logic.
\item QF\_UFIDL: uninterpreted functions and integer difference logic.
\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic.
\item QF\_UFLRA: uninterpreted functions and linear real arithmetic.
\item QF\_UFNRA: uninterpreted functions and nonlinear real arithmetic.
\item QF\_LRA: linear real arithmetic.
\item QF\_LIA: linear integer arithmetic.
\item QF\_NIA: nonlinear integer arithmetic.
\item QF\_AX: arrays with extensionality.
\item QF\_AUFLIA: arrays, uninterpreted functions and linear integer 
                  arithmetic.
\item QF\_BV: fixed-width bitvectors.
\item QF\_AUFBV: arrays, fixed-width bitvectors and uninterpreted
functions.
\item LRA: (quantified) linear real arithmetic.
\item AUFLIA$+p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns included.
\item AUFLIA$-p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns not included.
\item AUFLIRA: (quantified) arrays, uninterpreted functions and 
mixed linear integer and real arithmetic.
\item UFNIA$+p$: (quantified) uninterpreted functions and 
nonlinear integer arithmetic, patterns included.
\item AUFNIRA: (quantified) arrays, uninterpreted functions and 
mixed nonlinear integer and real arithmetic.
\end{itemize}

@@

The following scheme will be used to choose competition benchmarks
within each division.  Unknown-status benchmarks from SMT-LIB are
considered ineligible for competition and are not used.
%
Additionally, certain benchmarks deemed inappropriate for competition
may be cut by the organizers, and in some cases, representative subsets
of benchmarks from a certain source may be included for the selection
instead of all benchmarks from that source.
%
The selection
is implemented by our benchmark selection tool, source for which will
be available at \url{www.smtcomp.org}.

>>>>

\date{\small This version revised \the\year-\the\month-\the\day}

@@

Additionally, non-competitive divisions and tracks will not be exhibited as
part of the competition: at least two competitors must be entered
into a division for it to run as part of the competition.
If necessary, and based on final submissions, the organizers may elect to
combine competition divisions to make them competitive (such decisions will
be made with input from the community).

As in SMT-COMP 2010, the 2011 version will incorporate a small number of
random "fuzzer-generated" instances (see below) to help promote
attention to solver correctness.

It is important for competitors to track discussions on the SMT-COMP mailing
list, as clarifications and any updates to these rules will be posted there.

@@

\header{Timeouts.}
A time limit is set for the whole execution of each application
benchmark (consisting of multiple queries).  We anticipate the
timeout to be around 30~minutes.

@@

\begin{itemize}
\item QF\_UF: uninterpreted functions.
\item QF\_RDL: real difference logic.
\item QF\_IDL: integer difference logic.
\item QF\_UFIDL: uninterpreted functions and integer difference logic.
\item QF\_UFLIA: uninterpreted functions and linear integer arithmetic.
\item QF\_UFLRA: uninterpreted functions and linear real arithmetic.
\item QF\_UFNRA: uninterpreted functions and nonlinear real arithmetic.
\item QF\_LRA: linear real arithmetic.
\item QF\_LIA: linear integer arithmetic.
\item QF\_NRA: nonlinear real arithmetic.
\item QF\_NIA: nonlinear integer arithmetic.
\item QF\_AX: arrays with extensionality.
\item QF\_AUFLIA: arrays, uninterpreted functions and linear integer 
                  arithmetic.
\item QF\_BV: fixed-width bitvectors.
\item QF\_AUFBV: arrays, fixed-width bitvectors and uninterpreted
functions.
\item LRA: (quantified) linear real arithmetic.
\item AUFLIA$+p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns included.
\item AUFLIA$-p$: (quantified) arrays, uninterpreted functions and 
linear integer arithmetic, patterns not included.
\item AUFLIRA: (quantified) arrays, uninterpreted functions and 
mixed linear integer and real arithmetic.
\item UFNIA$+p$: (quantified) uninterpreted functions and 
nonlinear integer arithmetic, patterns included.
\item AUFNIRA: (quantified) arrays, uninterpreted functions and 
mixed nonlinear integer and real arithmetic.
\end{itemize}

@@

The following scheme will be used to choose competition benchmarks
within each division.  Unknown-status benchmarks from SMT-LIB are
considered ineligible for competition and are not used.
%
The selection
is implemented by our benchmark selection tool, source for which will
be available at \url{www.smtcomp.org}.
